Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massively Distributed Evolutionary Computation

### 2015-07-30 volunteer-clouds-ieee-ci-si.tex
some comments

\section{Introduction}

@@

The rest of the paper is organized as follows. Next we present the
state of the art in web-based distributed computation systems along
with attempts to predict and model its behavior.

\section{State of the art}
\label{sec:soa}

@@

\section{Description of the system}

\section{Conclusion}
The conclusion goes here.

% use section* for acknowledgment
\section*{Acknowledgment}

>>>>

%---------------------------------------------------------------
\section{Introduction}

@@

The rest of the paper is organized as follows: Next we present the
state of the art (Section \ref{sec:soa}) in web-based distributed 
computation systems along with attempts to predict and model its behavior. 
Then, a detailed description of the proposed system is presented 
in Section \ref{sec:description}, followed by the experiments and 
obtained results in Section \ref{sec:experiments}.
Finally, conclusions and future work are presented in Section \ref{sec:conclusion}.

%---------------------------------------------------------------
\section{State of the art}
\label{sec:soa}

@@

%---------------------------------------------------------------
\section{Description of the system}
\label{sec:description}

%---------------------------------------------------------------
\section{Experiments and obtained results}
\label{sec:experiments}

%---------------------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}

The conclusion goes here.

%---------------------------------------------------------------
% use section* for acknowledgment
\section*{Acknowledgment}
